### 2016-08-19 Theorem1_FP.tex
Proof 1,2 update

In $\game{3}(A)$, we replace the random functions used in
$\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from
$[m]$.  This change does not alter the behavior of the oracle, as the
random functions are (by the no-pointless-queries assumption on~$A$) always called on a new
value of~$x$.
%
Also, the $\QryOracle$ oracle now sets $\bad$ to $\true$ if the
queries indexed by the set $\mathcal{I}$ fail to be false-positives,
or if any of the remaining queries are false-positives. It can be
observed that the $\bad$ flag has no impact on the output of the
$\QryOracle$, nor does it affect  the value returned
by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
\Prob{\game{3}(A)=1}$ and
\[
\Prob{\game{3}(A)=1 \wedge \game{3}(A): \neg\bad} = \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}%\label{eq:1} \\
\]

@@

Before continuing the proof, a bit of intuition for the introduction
of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
set~$\mathcal{I}$ exactly predicts which of the $\QryOracle$ will be
false-positives (and, conversely, which will not be), then a
non-adaptive FP-finding adversary can ``guess'' which of~$A$'s queries require it
to return 1 when simulating the $\QryOracle$, and which require it to
return 0.  In this way, no queries ever actually need to be made.
Moving to a non-adaptive setting will allow us to connect to classical
results on the FP-rate of Bloom filters; more in a moment.

Now, consider $\Prob{\game{3}(A) : \neg\bad}$.  The indicated event
happens iff the $r$-set~$\calI$ contains exactly the indices of
$\QryOracle$-queries that are false-positives.  Since the value
of~$\bad$ does not alter the responses of~$\QryOracle$, the
set~$\mathcal{Z}$ output by~$A$ and the set~$\calI$ are independent.
Thus $\bad$ remains $\false$ after~$A$ halts with probability
$1/\dbinom{q}{r}$, and we have 
\begin{equation*}
\Prob{\game{4}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{3}(A)=1}
\end{equation*}

Recall that adversary~$A$ wins $\ExpCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.  We can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
Under these assumptions, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in \Cref{fig:D}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be the false positives; it simulates the~$\QryOracle$ by returning 1 on the guessed queries, and 0 otherwise; and it halts by outputting the set of guessed queries.  Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.

Note that $\tilde{B}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries are distinct and not elements of the original set~$S$, since we assume no pointless queries. Hence, so are the points $x_1,x_2,\ldots,x_r$ returned by~$D$.  Let $\calF_i$ be the event that~$x_i$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

@@

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $c \in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$\\
\nudge $\err \gets\err +1$\\
Return~$(v,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

@@

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.35}
{
$\adversaryv{D(S)}$\\[4pt]
$c \gets 0$, $\calX \gets \emptyset$\\
$\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S)$\\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Ret $(r,\err )$\\
When $A$ halts:\\
\nudge Ret $\calX$
}
\caption{\Cref{thm1}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\end{figure}

>>>>

In $\game{3}(A)$, we replace the random functions used in
$\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from
$[m]$.  This change does not alter the behavior of the oracle, as the
random functions are (by the no-pointless-queries assumption on~$A$) always called on a new
value of~$x$.
%
Also, the $\Test$ oracle now sets $\bad$ to $\true$ if the
queries indexed by the set $\mathcal{I}$ fail to be false-positives,
or if any of the remaining queries are false-positives. It can be
observed that the $\bad$ flag has no impact on the output of the
$\Test$, nor does it affect  the value returned
by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
\Prob{\game{3}(A)=1}$ and
\[
\Prob{\game{3}(A)=1 \wedge \game{3}(A): \neg\bad} = \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}%\label{eq:1} \\
\]

@@

Before continuing the proof, a bit of intuition for the introduction
of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
set~$\mathcal{I}$ exactly predicts which of the $\Test$ queries will be
false-positives (and, conversely, which will not be), then a
non-adaptive FP-finding adversary can ``guess'' which of~$A$'s queries require it
to return 1 when simulating the $\Test$, and which require it to
return 0.  In this way, no queries ever actually need to be made.
Moving to a non-adaptive setting will allow us to connect to classical
results on the FP-rate of Bloom filters; more in a moment.

Now, consider $\Prob{\game{3}(A) : \neg\bad}$.  The indicated event
happens iff the $r$-set~$\calI$ contains exactly the indices of
$\Test$-queries that are false-positives.  Since the value
of~$\bad$ does not alter the responses of~$\Test$, $\err$'s update
and the set~$\calI$ are independent.
Thus $\bad$ remains $\false$ after~$A$ halts with probability
$1/\dbinom{q}{r}$, and we have 
\begin{equation*}
\Prob{\game{4}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{3}(A)=1}
\end{equation*}

Recall that adversary~$A$ wins $\ExpCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive. % We can also assume that every point in $\calZ$ has already been queried to $\Test$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
%Under these assumptions,
So, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in \Cref{fig:D}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's.  Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.

Note that $\tilde{B}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries. Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I}$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

@@

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $c \in \mathcal{I}$ and $v = q(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $v \neq q(S)$ then \\
\nudge $\bad \gets \true$\\
if $v \neq q(S)$\\
\nudge $\err \gets\err +1$\\
Return~$(v,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

@@

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.35}
{
$\adversaryv{D(S)}$\\[4pt]
$c \gets 0$\\%, $\calX \gets \emptyset$\\
$\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S)$\\
When $A$ asks $\Test(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
%\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Ret $(r,\err )$\\
When $A$ halts:\\
\nudge Ret 1
}
\caption{\Cref{thm1}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\end{figure}

### 2016-08-19 Theorem2_FP.tex
Proof 1,2 update

\begin{proof}[\Cref{thm2}]
We use a game playing argument similar to \Cref{thm1} to prove this theorem. In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
\begin{equation}
\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
\end{equation}

@@

Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{B}_{\mathrm{ds}}$. As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game. So, 
\begin{equation*}
\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
\end{equation*}
Note that like $\tilde{B}_{\mathrm{lin}}$, $\tilde{B}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature. So, for a non-adaptive adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{B}_{\mathrm{ds}}$ as well. For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ as well as the elements returned by $D$ are distinct and not elements of the original set $S$. Also, since $\game{3}$ uses independent random functions, the event of getting a false positive is independent of the index of the query. So,
\begin{equation*}
\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{equation*}
\noindent
To summarize, we have
\[
\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. \hfill \qed

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $j = 1$ to $k$\\
\nudge $h_j(x) =\FK $\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $j=1$ to $k$\\
\nudge $h_j(x) = \rhoK $\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.55}{.3}
{
\underline{{$\game{2}(A)$},\fbox{$\game{3}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $c \in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$\\
\nudge $\err \gets\err +1$\\
Return~$(v,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
for $j = 1$ to~$k$\\
\nudge $v_j = a$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm2}: Game playing argument}\label{fig:Game}
\end{figure}

%\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$, and non-adaptive adversary $D$ simulating $\game{4}(A)$} 
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q)$:\\
\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
\nudge if $a \neq q(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$(a,\err )$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
%
%
\oracle{$\HashOracle(x)$}\\
\nudge Ret $\OK$, for $j\in[1,k]$\\
}
{
$\adversaryv{D^{\QryOracle, \calS}}$\\
$c \gets 0$, $\calX \gets \emptyset$\\
$\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S)$\\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Ret $(r,\err )$\\
When $A$ halts:\\
\nudge Ret $\calX $
}
%
%\oracle{$\QryOracle(x)$}\\
% Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
%\oracle{$\HashOracle(x)$}\\
%for $j = 1$ to~$k$\\
%\nudge $v_j = \rhoK $\\
%Ret $\left(v_1,\ldots,v_k\right)$
}
\caption{\Cref{thm2}: \bf{Left}:PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$.\bf{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
\end{figure}

>>>>

\begin{proof}[\Cref{thm2}]
We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem. In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
\begin{equation}
\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
\end{equation}

@@

Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{B}_{\mathrm{ds}}$. As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game. So, 
\begin{equation*}
\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
\end{equation*}
Note that like $\tilde{B}_{\mathrm{lin}}$, $\tilde{B}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature. So, for a non-adaptive adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{B}_{\mathrm{ds}}$ as well. For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$. Also, since $\game{3}$ uses independent random functions, the event of getting a false positive is independent of the index of the query. So,
\begin{equation*}
\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{equation*}
\noindent
To summarize, we have
\[
\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. \hfill \qed

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $j = 1$ to $k$\\
\nudge $h_j(x) =\FK $\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $j=1$ to $k$\\
\nudge $h_j(x) = \rhoK $\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.55}{.3}
{
\underline{{$\game{2}(A)$},\fbox{$\game{3}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $c \in \mathcal{I}$ and $v = q(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $v \neq q(S)$ then \\
\nudge $\bad \gets \true$\\
if $v \neq q(S)$\\
\nudge $\err \gets\err +1$\\
Return~$(v,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
for $j = 1$ to~$k$\\
\nudge $v_j = a$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm2}: Game playing argument}\label{fig:2TGame}
\end{figure}

%\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$, and non-adaptive adversary $D$ simulating $\game{4}(A)$} 
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q)$:\\
\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
\nudge if $a \neq q(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$(a,\err )$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
%
%
\oracle{$\HashOracle(x)$}\\
\nudge Ret $\OK$, for $j\in[1,k]$\\
}
{
$\adversaryv{D^{\TestOracle, \calS}}$\\
$c \gets 0$\\%, $\calX \gets \emptyset$\\
$\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S)$\\
When $A$ asks $\TestOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
%\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Ret $(r,\err )$\\
When $A$ halts:\\
\nudge Ret 1
}
%
%\oracle{$\TestOracle(x)$}\\
% Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
%\oracle{$\HashOracle(x)$}\\
%for $j = 1$ to~$k$\\
%\nudge $v_j = \rhoK $\\
%Ret $\left(v_1,\ldots,v_k\right)$
}
\caption{\Cref{thm2}: \bf{Left}:PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$.\bf{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
\end{figure}
